\documentclass[11pt,twoside]{reedthesis}
\usepackage{graphicx,latexsym} 
\usepackage{amssymb,amsthm,amsmath}
\usepackage{longtable,booktabs,setspace} 
\usepackage[hyphens]{url}
\usepackage{rotating}
\usepackage{natbib}
\usepackage[margin=1in]{geometry}
\usepackage{clrscode3e}
\usepackage{mathtools}
\usepackage{tikz}
\usepackage{float}
\usetikzlibrary{positioning,arrows}
\usepackage{setspace}
\usepackage{mathpazo}
\usepackage{framed}
\usepackage{varwidth}
\usepackage{enumitem}
\doublespacing
%\usepackage{tikz-berge}
%\usepackage{algorithm}
%\usepackage[noend]{algpseudocode}

 
\newcommand{\N}{\mathbb{N}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\R}{\mathbb{R}}
\renewcommand{\'}{^{'}}
\renewcommand{\gets}{:=}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}[chapter]

\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{lemma}[theorem]{Lemma}


\title{The Hungarian Algorithm and the Primal-Dual Method}
\author{Zachary Sean Campbell}
\date{May 2018}
\division{Mathematics and Natural Sciences}
\advisor{James D. Fix}
\department{Mathematics}
\setlength{\parskip}{0pt}

%% The fun begins:
\begin{document}

    \maketitle
    \frontmatter % this stuff will be roman-numbered
    \pagestyle{empty} % this removes page numbers from the frontmatter

\chapter*{Acknowledgements}
Accomplishments are not made in isolation. I have received a significant amount of help along the way 
from many people, too many to list and give due credit. I use this page to thank all of you now. 
I most definitely would not have gotten this far without those of you who have supported me. Thank you.

\tableofcontents
\chapter*{Abstract}
This thesis explores the relationship between problems in combinatorial optimization 
and those in linear programming. The former field of study is often introduced to students in an 
introductory course on discrete mathematics or algorithms, while the latter is often reserved for 
upper-division algorithms courses. 
Regardless, we focus on combinatorial problems typically introduced in an algorithms course and how 
they relate to the field of linear programming. In particular, we look at various matching problems 
on bipartite graphs and their associated linear programs. In doing so, we explore the fruitful 
intersection of these two fields by looking at the development of algorithms that solve combinatorial 
problems using theoretical results from linear programming.

\chapter*{}
``Deep in the human unconscious is a pervasive need for a logical universe that makes sense. But the 
real universe is always one step beyond logic.''

- Frank Herbert, \emph{Dune}
\mainmatter % here the regular arabic numbering starts
\pagestyle{fancyplain} % turns page numbering back on

\chapter*{Introduction}
        \addcontentsline{toc}{chapter}{Introduction}
	\chaptermark{Introduction}
	\markboth{Introduction}{Introduction}

	\input{introduction.tex}
	
\chapter{Matchings and Linear Programming}

\input{ch1_thesis.tex}

\chapter{Vertex Cover and Duality Theory}

\input{ch2_thesis.tex}

\chapter{The Hungarian Algorithm}

\input{ch3_thesis.tex}

\chapter{The Primal-Dual Method and Auction Algorithms}

\input{ch4_thesis.tex}
	

\backmatter % backmatter makes the index and bibliography appear properly in the t.o.c...

\nocite{*}
\bibliographystyle{plain}
\bibliography{thesis_bib}

\end{document}
